### 2021-02-24 notes/notes.tex

Context inference can work through context-specific (possibly unreliable) cues,
or through the dynamics themselves, using prediction error as the force behind
inference. Let us assume that both parts are present in the observation
$\theta_t$. In this case, the inferred generalized state is given by
$q(z_t | \theta_t, \theta_{t-1}, a_{t-1}) \propto p(\theta_t |
z_t)p(z_t|\theta_{t-1}, a_{t-1})$.

>>>>

Context inference can work through context-specific (possibly unreliable) cues,
or through the dynamics themselves, using prediction error as the force behind
inference. Let us assume that both parts are present in the observation
$\theta_t$. In this case, the inferred generalized state is given by
\[
  q(z_t | \theta_t, \theta_{t-1}, a_{t-1}) \propto p(\theta_t | z_t)p(z_t|\theta_{t-1}, a_{t-1})
\]

Additionally, after having inferred the current state, motor adaptation is given by
\[
q(\gamma | z_t, z_{t-1}, a_{t-1}) \propto p(z_t | z_{t-1}, a_{t-1}, \gamma)p(z_{t-1})p(\gamma)
\]

where $\gamma$ are the parameters of the internal model for the dynamics,
i.e. the function $f: (z_t, a_t) \rightarrow z_{t+1}$, which determines the beliefs of
the agent as to how the system evolves after having taken action $a_t$.
